---
title: "Reproducing Haplotype Regression From Hiltpold2020"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Reproducing Haplotype Regression From Hiltpold2020}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
# initialize Mendeley-Object
met <- rmdhelp::MendeleyExportToolR6$new(ps_this_rmd_file = ifelse(rstudioapi::isAvailable(),
    rstudioapi::getActiveDocumentContext()$path, rprojroot::thisfile()))
```

```{r setup, eval=FALSE}
library(haploreg)
```

# Disclaimer
The computations done in `r met$add('Hiltpold2020')` are tried to be reproduced here. The R-code used for the computations is analysed. 


# Include Material From Paper
The following commands are only done once to have the material from the paper available for reproducing the results. In the section of 'Supporting Information' the following two links are given 

* S1 Data: Data of 794 bulls used to detect the QTL on BTA6: https://doi.org/10.1371/journal.pgen.1008804.s009

```{r s1-data-download, eval=FALSE}
# prepare data download directory
download_dir <- file.path(here::here(), "inst", "extdata","hiltpold2020")
if (! fs::dir_exists(download_dir)) fs::dir_create(path = download_dir)
s1_data_url <- "https://doi.org/10.1371/journal.pgen.1008804.s009"
s1_data_zip <- file.path(download_dir, "S1_Data.zip")
download.file(url = s1_data_url, destfile = s1_data_zip)
s2_data_url <- "https://doi.org/10.1371/journal.pgen.1008804.s010"
s2_data_zip <- file.path(download_dir, "S2_Data.zip")
download.file(url = s2_data_url, destfile = s2_data_zip)
```

